---
title: getting xgboost tweedie prediction from link
author: simon
date: '2020-05-21'
slug: getting-xgboost-tweedie-prediction-from-link
categories: []
tags: []
keywords:
  - tech
---



```{r setup, include =F, echo =F}
#
# TODO : valider ceci : Chunk options must be written in one line; no line breaks are allowed inside chunk options;
# https://yihui.name/knitr/options/
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = FALSE,
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      fig.align= "center",
                      fig.width = 10,
                      highlight = TRUE,
                      cache = FALSE,
                      cache.lazy = FALSE) # fixes long vecto rnot supported quand on cache des gros éléments https://stackoverflow.com/questions/39417003/long-vectors-not-supported-yet-error-in-rmd-but-not-in-r-script
```

I've stumbled on something.. interesting.  

To get the prediction for a Tweedie GLM, we take the link value then do exp(link), but to get prediction from an xgboost tweedie , we take the "link" value then do exp(link)/ 2 , dividing the result by 2.  

Is this normal?   Below is a quick demo showing how I get the predictions for a 3-trees xgboost and a glm.

the code has been  modified from the tweedie regression demo in the xgboost repository: https://github.com/dmlc/xgboost/blob/master/R-package/demo/tweedie_regression.R



First, fit xgboost model and look at the trees :
```{r}
library(xgboost)
library(data.table)
library(cplm) # for insurance data
library(statmod) # for tweedie glm
data(AutoClaim)

# auto insurance dataset analyzed by Yip and Yau (2005)
dt <- data.table(AutoClaim)

# exclude these columns from the model matrix
exclude <-  c('POLICYNO', 'PLCYDATE', 'CLM_FREQ5', 'CLM_AMT5', 'CLM_FLAG', 'IN_YY')

# retains the missing values
# NOTE: this dataset is comes ready out of the box
options(na.action = 'na.pass')
x <- sparse.model.matrix(~ . - 1, data = dt[, -exclude, with = F])
options(na.action = 'na.omit')

# response
y <- dt[, CLM_AMT5]

d_train <- xgb.DMatrix(data = x, label = y, missing = NA)

# the tweedie_variance_power parameter determines the shape of
# distribution
# - closer to 1 is more poisson like and the mass
#   is more concentrated near zero
# - closer to 2 is more gamma like and the mass spreads to the
#   the right with less concentration near zero

params <- list(
  objective = 'reg:tweedie',
  eval_metric = 'rmse',
  tweedie_variance_power = 1.4,
  max_depth = 2,
  eta = 1)
set.seed(42)
bst <- xgb.train(
  data = d_train,
  params = params,
  maximize = FALSE,
  watchlist = list(train = d_train),
  nrounds = 3)


var_imp <- xgb.importance(attr(x, 'Dimnames')[[2]], model = bst)

preds <- predict(bst, d_train)

rmse <- sqrt(sum(mean((y - preds)^2)))

xgb.plot.tree(model = bst)
```

Manually extract the values for the first record :
```{r}
x[1,]
```

travtime < 102, bluebook <61645 -->tree #1 value= 2.49922585
revolkedyes <  -9.53674316e-07,   npolicy < 5.5 --> tree #2  value= 2.48586464
REVOLKEDYes <  -9.53674316e-07, areaurban >  -9.53674316e-07 --> tree #3 value =  2.36028123


```{r}
link_gbm <-  2.49922585 +2.48586464+  2.36028123
link_gbm


```

Take exp(link_gbm), divide by 2 (question: why??)
```{r}
exp(link_gbm ) / 2
```

Compare with prediction from xgboost .

```{r}
 predict(bst, d_train)[1]
```

Let's do the same with a GLM:  
```{r}
dt2 <-  dt[, -exclude, with = F]
dt2$CLM_AMT5 <-  dt$CLM_AMT5

tweedie_fit <-
  glm(CLM_AMT5 ~ .,
      family=tweedie(var.power=1.4, link.power=0),
      data = dt2)
 
summary(tweedie_fit)
```
Manually get the link value for the first record

```{r}
dt2[1,]
```
link =
```{r}
link_glm <- tweedie_fit$coefficients["(Intercept)"] +
  14 * tweedie_fit$coefficients["TRAVTIME"] +
  14230 * tweedie_fit$coefficients["BLUEBOOK"] +
  11 * tweedie_fit$coefficients["RETAINED"]  +
  1 * tweedie_fit$coefficients["NPOLICY"] +
  1 * tweedie_fit$coefficients["CAR_TYPESedan"] +
  1 * tweedie_fit$coefficients["RED_CARyes"] +
  3 * tweedie_fit$coefficients["MVR_PTS"] +
  60 * tweedie_fit$coefficients["AGE"] +
  11 * tweedie_fit$coefficients["YOJ"] +
  67349 * tweedie_fit$coefficients["INCOME"] +
  1 * tweedie_fit$coefficients["GENDERM"] +
  1 * tweedie_fit$coefficients["JOBCLASSProfessional"] +
  1 * tweedie_fit$coefficients["MAX_EDUCPhD"] +
  18 * tweedie_fit$coefficients["SAMEHOME"] +
  1 * tweedie_fit$coefficients["AREAUrban"]

link_glm
```

prediction is exp(link_glm)
```{r}
exp(link_glm)
```

compare with link and  prediction from glm ... yes, it's identical


```{r}
predict(tweedie_fit, type="link")[1]
```

```{r}
predict(tweedie_fit, type="response")[1]
```


